---
title: "topogram"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{topogram}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  message = FALSE,
  warning = FALSE
)
```

```{r setup}
library(topogram)
library(htmltools)
```

Create continuous area cartograms with [`cartogram-chart`](https://github.com/vasturiano/cartogram-chart):

```{r}
topogram(world, value = "pop_est")
```

First argument is an `sf` object containing geometries to visualize, the specify a numeric variable to use to distort those geometries.

You can use a `glue` string to be used in tooltip, specify geographic projection to use, add labs and legend, ...

```{r}
world %>% 
  topogram( 
    value = "pop_est", 
    label = "{name}: {format(pop_est, big.mark = ',')}",
    palette = scales::col_bin("Blues", bins = 20, domain = NULL)
  ) %>% 
  topogram_legend(
    title = "Population",
    formatter = scales::label_comma()
  ) %>% 
  topogram_labs(
    title = "World population",
    subtitle = "Population estimate for 2017",
    caption = tagList(
      "Data source:",
      tags$a(
        href = "https://www.naturalearthdata.com/",
        "NaturalEarth"
      )
    )
  )
```


In Markdown documents, you can use `topogram_select()`, to add a menu tu update variable used to distort topology. First add select menu:

```{r}
topogram_select(
  topogramId = "ID",
  sfobj = world,
  values = list(
    "Population" = "pop_est",
    "GDP" = "gdp_md_est", 
    "CO2 emissions (1990)" = "co2_emissions_1990", 
    "CO2 emissions (2020)" = "co2_emissions_2020", 
    "Share of electricity production from renewables" = "renewables_percent_electricity"
  ),
  label = "{name} : {value}"
)
```

Then create topogram:

```{r}
topogram(
  sfobj = world,
  value = "pop_est", 
  label = "{name} : {value}",
  elementId = "ID"
)
```

